---
title: "Practicum Data Cleaning"
author: "Anh Do"
date: "November 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F)
```

```{r library}
library(tidyverse)
library(lubridate)
library(ggthemes)
library(data.table)
library(scales)
```

```{r new, cache=T}
newwo = read_csv("../Dude_data/workorder_grouped.csv", guess_max = 1800000)

#newwo = read_csv("C:/Users/andyt/Desktop/KSB-621/Dude_data/workorder_grouped.csv")
```

1. Requested Date

#For time series, useful for descriptive but may not be useful for predictive unless we do per account

```{r requestdate}
requested = newwo %>% 
  mutate(yearrequested = year(daterequested),
         monthrequested = month(datecreated),
         dayrequested = day(datecreated)) %>%
  filter(yearrequested < 2020, yearrequested > 2000) %>%
  mutate(ymrequested = make_date(yearrequested, monthrequested),
         ymdrequested = make_date(yearrequested, monthrequested, dayrequested)) 

request_count = requested %>%
  group_by(ymrequested) %>%
  summarize(count = n())
request_count

request_craft = requested %>%
  group_by(craftgroup, ymrequested) %>%
  summarise(count = n()) 
request_craft

request_customer = requested %>%
  group_by(ymdrequested, dudecustomerid) %>%
  summarize(count = n()) %>%
  arrange(dudecustomerid)
request_customer
```

```{r requestts}
request_craft %>% 
  ggplot(aes(x=ymrequested, y=count)) +
  geom_line() + theme_few()
```

2. Cost per Craft group

```{r cost}
cost_craft = newwo %>% filter(actualcosts < 1000000000) %>%
  group_by(craftgroup) %>%
  summarise(TotalCost = round(sum(actualcosts)/1000000, digits = 4)) %>%
  arrange(desc(TotalCost)) %>% 
  ggplot(aes(x=reorder(craftgroup, TotalCost), y=TotalCost)) + 
  geom_bar(stat="identity") +
  guides(fill=F) +
  coord_flip() +
  theme_few() +
  labs(title="Total Cost per Craft Group", 
       y="Total Cost (in Million)", 
       x="") +
  theme(title = element_text(face="bold"), 
        axis.title = element_text(face="bold"),
        panel.border = element_blank(), 
        axis.line.x = element_line(colour="grey80"), 
        axis.line.y = element_line(colour="grey80"),
        axis.ticks  = element_blank()) +
  scale_y_continuous(labels = dollar)
  
cost_craft

high_furniture_cost = newwo %>% filter(craftgroup == "FURNITURES/UTILITIES/APPLIANCES") %>%
  group_by(craftdescription) %>%
  summarise(TotalCost = round(sum(actualcosts)/1000000, digits = 4)) %>%
  arrange(desc(TotalCost)) %>% 
  filter(TotalCost > 10) %>%
  ggplot(aes(x=reorder(craftdescription, TotalCost), y=TotalCost)) + 
  geom_bar(stat="identity") +
  guides(fill=F) +
  coord_flip() +
  theme_few() +
  labs(title="Most expensive crafts under Furniture/Utilities/Appliances", 
       y="Total Cost (in Million)", 
       x="") +
  theme(title = element_text(face="bold", size = 10), 
        axis.title = element_text(face="bold"),
        panel.border = element_blank(), 
        axis.line.x = element_line(colour="grey80"), 
        axis.line.y = element_line(colour="grey80"),
        axis.ticks  = element_blank()) +
  scale_y_continuous(labels = dollar)

```

3. Cost per Asset ID

Most assets cost less than $1000.

```{r statuscount}
cost_asset = newwo %>%
  filter(!is.na(assetid), assetid > 0) %>%
  group_by(assetid) %>%
  summarise(TotalCost = round(sum(actualcosts))) %>%
  arrange(desc(TotalCost)) 

print(paste("There are", length(unique(cost_asset$assetid)), "unique assets."))

asset_cost_histogram = cost_asset %>% 
  ggplot(aes(x = TotalCost)) + 
  geom_histogram() + 
  theme_few() +
  labs(title="Asset cost Distribution", 
       y="Total Cost", 
       x="Number of Assets")

expensive_asset = cost_asset %>% 
  filter(TotalCost >= 100000) %>% 
  ggplot(aes(x = TotalCost)) + 
  geom_histogram() + 
  theme_few() +
  labs(title="Distribution of Most expensive Asset", 
       y="Total Cost (in Million)", 
       x="Number of Assets")

normal_asset = cost_asset %>% 
  filter(TotalCost < 2000) %>% 
  ggplot(aes(x = TotalCost)) + 
  geom_histogram() + 
  theme_few() +
  labs(title="Distribution of Assets with total cost less than $2000", 
       y="Total Cost", 
       x="Number of Assets")

asset_cost_histogram
expensive_asset
normal_asset
```

4. Count Reactive/Preventive Craft Group

#preventive is one of the craft groups which may be confusing

```{r pmcraft}
pm_craft = newwo %>%
  group_by(craftgroup) %>%
  summarise(Count = round(sum(ispreventmaint)/1000, digits = 2)) %>%
  arrange(desc(Count)) %>% 
  ggplot(aes(x=reorder(craftgroup, Count), y=Count)) + 
  geom_bar(stat="identity") +
  guides(fill=F) +
  coord_flip() +
  theme_few() +
  labs(title="Number of Preventive Maintenance per Craft Group", 
       y="Total Cost (in Thousand)", 
       x="") +
  theme(title = element_text(face="bold", size=10), 
        axis.title = element_text(face="bold"),
        panel.border = element_blank(), 
        axis.line.x = element_line(colour="grey80"), 
        axis.line.y = element_line(colour="grey80"),
        axis.ticks  = element_blank()) +
  scale_y_continuous(labels = dollar)
pm_craft
```

5. Count Reactive/Preventive Asset ID

We look at the first 6 assets with the highest number of preventive maintenance work orders, and the first 6 assets with the highest average cost per preventive maintenance work orders, since these are the outliers. We plan to perform time series for these 12.

```{r pmasset}
pm_asset = newwo %>%
  filter(!is.na(assetid), assetid > 0, ispreventmaint == 1) %>%
  group_by(assetid) %>%
  summarise(Count = sum(ispreventmaint),
            AverageCost = round(mean(actualcosts), digits = 4)) %>%
  arrange(assetid)

plot(pm_asset$Count, pm_asset$AverageCost, xlab = "Number of preventive maintenance work orders", ylab = "Average Cost in Dollar")

pm_asset %>% 
  arrange(desc(Count)) %>%
  head()

pm_asset %>%
  arrange(desc(AverageCost)) %>%
  head()  

```

by priority description, by craft, by efficiency (predict efficiency based on craftgroup, priority, ispreventmaint - regression, tree)

```{r date}
requested = newwo %>% 
  mutate(yearrequested = year(daterequested),
         monthrequested = month(daterequested),
         dayrequested = day(daterequested)) %>%
  filter(yearrequested < 2020, yearrequested > 2000) %>%
  mutate(ymrequested = make_date(yearrequested, monthrequested),
         ymdrequested = make_date(yearrequested, monthrequested, dayrequested)) %>%
  mutate(yearcompleted = year(actualcompletiondate),
         monthcompleted = month(actualcompletiondate),
         daycompleted = day(actualcompletiondate)) %>%
  filter(yearcompleted < 2020, yearcompleted > 2000) %>%
  mutate(ymcompleted = make_date(yearcompleted, monthcompleted),
         ymdcompleted = make_date(yearcompleted, monthcompleted, daycompleted))

```

```{r priorityts}
priority = requested %>% select(craftdescription, craftgroup, daterequested, datecreated, actualcompletiondate, laststatuschange, currentstatus, prioritydescription, ispreventmaint, ymrequested, ymcompleted) %>%
  filter(currentstatus != "Others") %>%
  filter(!(prioritydescription %in% c("-", "TBD", "Safety", "unknown", "Some Production Loss", "System Available", "Spare Time"))) %>%
  filter(!is.na(daterequested), !is.na(datecreated), !is.na(laststatuschange)) %>%
  mutate(createffi = as.numeric(round((datecreated - daterequested)/3600, digits = 2)),
         totaleffi = as.numeric(round((actualcompletiondate - daterequested)/3600, digits = 2))) %>%
  filter(totaleffi >= 0, createffi >= 0)

priority
```



```{r}
#my work starts here

#check how many craft groups there are
#build a model for one craft group, copy & paste for others
unique(priority$craftgroup)

#average create efficiency
avg_cr_ef <- mean(priority$createffi)

#create efficiency as a percentage of the avg create efficiency
priority %>%
  mutate(cr_ef_percent = (createffi/(avg_cr_ef)))-> priority_1

#building the model to be applied to all other craft groups
priority_1 %>%
  filter(craftgroup == "PLUMBING/RESTROOM") -> plumbing_rest_prio
```

```{r}
#necessary libraries loaded
library(workflows)
library(parsnip)
library(recipes)
library(yardstick)
library(glmnet)
library(tidyverse)
library(tidyquant)
library(timetk)

plum_rest <- plumbing_rest_prio %>%
    select(datecreated, cr_ef_percent) %>%
    rename(date  = datecreated,
           value = cr_ef_percent)

plum_rest %>%
    ggplot(aes(x = date, y = value)) +
    geom_rect(xmin = ymd("2016-01-01"),
              xmax = ymd("2019-12-31"),
              ymin = 0, ymax = max(plum_rest$value),
              fill = palette_light()[[4]], alpha = 0.01) +
    geom_point(alpha = 0.5, color = palette_light()[[1]]) +
    labs(title = "create efficiency %", x = "") +
    theme_tq()
```

```{r}
#split into train and test sets
plum_rest %>% 
  filter(date < ymd("2016-01-01")) -> train_tbl

plum_rest %>% 
  filter(date >= ymd("2016-01-01")) -> test_tbl

#adding time series signature
recipe(value ~ ., data = train_tbl) %>%
    step_timeseries_signature(date) -> recipe_spec_timeseries

bake(prep(recipe_spec_timeseries), new_data = train_tbl)

recipe_spec_timeseries %>%
    step_rm(date) %>%
    step_rm(contains("iso"), contains("minute"), contains("hour"),
            contains("am.pm"), contains("xts")) %>%
    step_normalize(contains("index.num"), date_year) %>%
    step_dummy(contains("lbl"), one_hot = TRUE) %>%
    step_ns(date_index.num, deg_free = 3) -> recipe_spec_final

bake(prep(recipe_spec_final), new_data = train_tbl)

linear_reg(mode = "regression", penalty = 0.001, mixture = 0.5) %>%
    set_engine("glmnet") -> model_spec_glmnet

workflow() %>%
    add_recipe(recipe_spec_final) %>%
    add_model(model_spec_glmnet) -> workflow_glmnet

workflow_glmnet %>% 
  fit(data = train_tbl) -> workflow_trained

workflow_trained %>% 
    predict(test_tbl) %>%
    bind_cols(test_tbl) -> prediction_tbl


#new plot with prediction v actual side by side for 2016 onwards
#to see how good the model we built was against actual data
plum_rest %>%
    ggplot(aes(x = date, y = value)) +
  #can we somehow modify this so the test region is shaded
  #and train region is not
  #same problem happens in original scatterplot
    #geom_rect(xmin = ymd("2016-01-01"),
              #xmax = ymd("2019-12-31"),
              #ymin = 0, ymax = max(plum_rest$value),
              #fill = palette_light()[[4]], alpha = 0.01) +
    geom_point(alpha = 0.5, color = palette_light()[[1]]) +
    labs(title = "create efficiency %", x = "") +
    geom_point(aes(x = date, y = .pred), data = prediction_tbl, 
               alpha = 0.5, color = palette_light()[[2]]) +
    theme_tq()





```

```{r}
#forecasting future data
# Extract create efficiency index
plum_rest %>% 
  tk_index() -> idx
idx %>%
  # Get time series summary from index
  tk_get_timeseries_summary()-> bikes_summary


idx %>% 
  tk_make_future_timeseries(n_future = 18000) -> idx_future

tibble(date = idx_future)  -> future_tbl

workflow_glmnet %>% 
    fit(data = plum_rest) %>%
    predict(future_tbl) %>%
    bind_cols(future_tbl) -> future_predictions_tbl 

#forecasting for next 6 months scatterplot
plum_rest %>%
    ggplot(aes(x = date, y = value)) +
  #can we somehow modify this so the test region is shaded
  #and train region is not
  #same problem happens in original scatterplot
    #geom_rect(xmin = ymd("2016-01-01"),
              #xmax = ymd("2019-12-31"),
              #ymin = 0, ymax = max(plum_rest$value),
              #fill = palette_light()[[4]], alpha = 0.01) +
    geom_point(alpha = 0.5, color = palette_light()[[1]]) +
    labs(title = "create efficiency %", x = "") +
     geom_point(aes(x = date, y = .pred), data = future_predictions_tbl,
               alpha = 0.5, color = palette_light()[[2]]) +
    geom_smooth(aes(x = date, y = .pred), data = future_predictions_tbl,
                method = 'loess') + 
    theme_tq()

```

```{r}
#this is the function that generates the future create and predict efficiency  using glm loess

avg_cr_ef <- mean(priority$createffi)
avg_tot_ef <- mean(priority$totaleffi)

#create efficiency as a percentage of the avg create efficiency
priority %>%
  mutate(cr_ef_percent = (createffi/(avg_cr_ef)))-> priority_2

priority_2 %>%
  mutate(tot_ef_percent = (totaleffi/(avg_tot_ef)))-> priority_3

predict_cr_effi <- function(df)
{
library(workflows)
library(parsnip)
library(recipes)
library(yardstick)
library(glmnet)
library(tidyverse)
library(tidyquant)
library(timetk)

df_1 <- df %>%
    select(datecreated, cr_ef_percent) %>%
    rename(date  = datecreated,
           value = cr_ef_percent)

df_1 %>% 
  tk_index() -> idx
idx %>%
  # Get time series summary from index
  tk_get_timeseries_summary()-> bikes_summary


idx %>% 
  tk_make_future_timeseries(n_future = 18000) -> idx_future

tibble(date = idx_future)  -> future_tbl

workflow_glmnet %>% 
    fit(data = df_1) %>%
    predict(future_tbl) %>%
    bind_cols(future_tbl) -> future_predictions_tbl 

#forecasting for next 6 months scatterplot
df_1 %>%
    ggplot(aes(x = date, y = value)) +
  #can we somehow modify this so the test region is shaded
  #and train region is not
  #same problem happens in original scatterplot
    #geom_rect(xmin = ymd("2016-01-01"),
              #xmax = ymd("2019-12-31"),
              #ymin = 0, ymax = max(plum_rest$value),
              #fill = palette_light()[[4]], alpha = 0.01) +
    geom_point(alpha = 0.5, color = palette_light()[[1]]) +
    labs(title = "create efficiency %", x = "") +
     geom_point(aes(x = date, y = .pred), data = future_predictions_tbl,
               alpha = 0.5, color = palette_light()[[2]]) +
    geom_smooth(aes(x = date, y = .pred), data = future_predictions_tbl,
                method = 'loess') + 
    theme_tq()

}

predict_tot_effi <- function(fd)
{
library(workflows)
library(parsnip)
library(recipes)
library(yardstick)
library(glmnet)
library(tidyverse)
library(tidyquant)
library(timetk)

 fd %>%
    select(datecreated, tot_ef_percent) %>%
    rename(date  = datecreated,
           value = tot_ef_percent)-> fd_1

fd_1 %>% 
  tk_index() -> idx
idx %>%
  # Get time series summary from index
  tk_get_timeseries_summary()-> bikes_summary


idx %>% 
  tk_make_future_timeseries(n_future = 18000) -> idx_future

tibble(date = idx_future)  -> future_tbl

workflow_glmnet %>% 
    fit(data = fd_1) %>%
    predict(future_tbl) %>%
    bind_cols(future_tbl) -> future_predictions_tbl 

#forecasting for next 6 months scatterplot
fd_1 %>%
    ggplot(aes(x = date, y = value)) +
  #can we somehow modify this so the test region is shaded
  #and train region is not
  #same problem happens in original scatterplot
    #geom_rect(xmin = ymd("2016-01-01"),
              #xmax = ymd("2019-12-31"),
              #ymin = 0, ymax = max(plum_rest$value),
              #fill = palette_light()[[4]], alpha = 0.01) +
    geom_point(alpha = 0.5, color = palette_light()[[1]]) +
    labs(title = "create efficiency %", x = "") +
     geom_point(aes(x = date, y = .pred), data = future_predictions_tbl,
               alpha = 0.5, color = palette_light()[[2]]) +
    geom_smooth(aes(x = date, y = .pred), data = future_predictions_tbl,
                method = 'loess') + 
    theme_tq()

}

predict_cr_effi()
predict_tot_effi()
priority_3 %>%
  filter(craftgroup == "PLUMBING/RESTROOM") -> plumbing_rest_prio
```

